`phyr`: An R package for model-based phylogenetic analyses

### 2018-11-07 ms.Rmd
update ms [skip ci]

```{r knitr_options, include = FALSE}
if(!require("xfun")) devtools::install_github("yihui/xfun")
if(!require("phyr")) devtools::install_github("daijiang/phyr")
xfun::pkg_attach2(c("phyr", "knitr", "kableExtra", "kableExtra", "tidyverse"))
# opts_knit$set(root.dir = normalizePath("../"))
opts_chunk$set(fig.align='center', cache = FALSE, warning = FALSE, 
               message = FALSE, echo = TRUE)
options(digits = 3, width = 88, knitr.kable.NA = '')

@@

`cor_phy`

`binaryPGLMM`

@@

The original code for `communityPGLMM` were imported from the R package `pez` [@pearse2015pez]. Its theorectical background was presented in @ives2011generalized. We improved both the user interface and the speed of `communityPGLMM` here. Function `pez::communityPGLMM` requires user-prepared random terms while `phyr::communityPGLMM` makes this step much easier by adapting formula syntax for mixed models provided by the R package `lme4` [@bates2015lme4].

### ML

### Bayes

### Other help functions

Such as `communityPGLMM.plot.re()`. We can use it to show the design matrices' structures of random terms in `communityPGLMM()`. An example can be shown in Figure \@ref(fig:reStructure).

@@

>>>>

```{r knitr_options, include = FALSE}
if(!require("xfun")) install.packages("xfun")
if(!require("phyr")) devtools::install_github("daijiang/phyr")
xfun::pkg_attach2(c("phyr", "knitr", "kableExtra", "kableExtra", "tidyverse"))
# opts_knit$set(root.dir = normalizePath("../"))
opts_chunk$set(fig.align='center', cache = FALSE, warning = FALSE, 
               message = FALSE, echo = TRUE)
options(digits = 3, width = 88, knitr.kable.NA = '')

@@

Two functions (`cor_phy` and `binaryPGLMM`) were included in this group. Both of them were included in the R package `ape` [@ape2018] orginally.

`cor_phy`: ... (Lucas?)

`binaryPGLMM`: only 1 value per species, right?

@@

The original code for `communityPGLMM` were imported from the R package `pez` [@pearse2015pez]. Its theorectical background was presented in @ives2011generalized. We made several important updates here. First, function `pez::communityPGLMM` requires user-prepared random terms while `phyr::communityPGLMM` makes this step much easier by adapting formula syntax for mixed models provided by the R package `lme4` [@bates2015lme4]. To specify a random term with design matrix derived from a phylogenetic variance-covariance matrix, we can append two underscores (`__`) to the group variable. For example, `(1 | sp__)` will create *two* random terms: one with and one without (i.e. identity matrix) phylogenetic design matrix. To test whether closely related species are more or less likely to co-occur in the same site, we can use `(sp__@site)` along with the argument `repulsion = TRUE` (overdispersion) or `repulsion = FALSE` (underdispersion; default). Second, we extended `communityPGLMM` to work with Binomial and Poisson distributed data while `pez::communityPGLMM` only allows Binary and Gaussian data. Third, we provided both Maximum likelihood and Bayesian approaches to fit PGLMMs. Users can choose the approach via `bayes = TRUE` or `bayes = FALSE` (default). The Bayesian PGLMMs were fitted with integrated nested Laplace approximations (INLA) via the R package `r-inla` [@rue2009approximate]. Fourth, we improved the speed of `communityPGLMM` by rewriting key functions in c++.

The function `communityPGLMM` is modularized (prepare data, design matrix, optimization, etc.). (Too much details??)

The class of the model object returned is `communityPGLMM`, which has multiple methods (e.g., `print`, `summary`) associated with. Use `methods(class = 'communityPGLMM')` to see the full list. To visualize the design matrices' structures of random terms in the model object, we can use `communityPGLMM.plot.re()`. An example can be shown in Figure \@ref(fig:reStructure). It is also optional to simulate and plot data based on the design matrices with the argument `show.sim.image = TRUE`.

@@

Simulation of data; then apply the main functions.

# Limitations

`communityPGLMM` requires columns `site` and `sp`.
